Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint

### 2020-03-18 analysis/SOPO/2-trawl-no-covs-model.Rmd
remove sci notation

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params:
    # species: "Redbanded Rockfish"
    # species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    species: "Pacific Sand Lance"
    # species: "Pacific Herring"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    start_year: 2003
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    covs: "-no-covs-300" # covariate string used to name model rds
    AR1: TRUE
    fixed_spatial: FALSE
    update_model: FALSE
    update_model_check: FALSE #TRUE
    update_predictions: FALSE #TRUE
    update_index: FALSE
---

@@

theme_set(
    gfplot::theme_pbs(base_size = 14) 
)
```

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params:
    # species: "Redbanded Rockfish"
    species: "North Pacific Spiny Dogfish"
    # species: "Pacific Ocean Perch"
    # species: "Bocaccio"
    # species: "Yelloweye Rockfish"
    # species: "Pacific Sand Lance"
    # species: "Pacific Herring"
    # region: "All synoptic surveys"
    region: "Both odd year surveys"
    start_year: 2003
    knots: 300
    covariates: "" # +as.factor(ssid)
    #additional fixed-effect covariates
    covs: "-no-covs-300" # covariate string used to name model rds
    AR1: TRUE
    fixed_spatial: FALSE
    update_model: FALSE
    update_model_check: FALSE #TRUE
    update_predictions: FALSE #TRUE
    update_index: FALSE
---

@@

# options(scipen = 999)
theme_set(
    gfplot::theme_pbs(base_size = 14) 
)
```
